Spatial Relational Models for Neural Circuit Discovery

### 2013-10-21 docs/techreport.tex
updates including the c. elegans results.

\subsubsection{results}
They are crappy.

@@

>>>>

\subsubsection{Results}
We used two relations, one for chemical and one for electrical synapses. 
We binarize the synapse counts at greater than zero.

\begin{figure}
  \centering 
  \begin{subfigure}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{celegans/celegans.2r.ld.00.data-fixed_100_200-anneal_slow_400.0.clusters.pdf}
    \caption{Logistic-Distance Bernoulli}
    \label{fig:celegans:clusters:ld}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{celegans/celegans.2r.ndfw.00.data-fixed_100_200-anneal_slow_400.0.clusters.pdf}
    \caption{Normal-Distance Fixed-Width}
    \label{fig:celegans:clusters:ndfw}
  \end{subfigure}
  \caption{C. elegans clusters. }
  \label{fig:celegans:clusters}
\end{figure}

They are crappy.

@@

\todo{should we use the exponentail-distance-count likelihood?}
